Interval Probability for Fuzzy Quantum Theories

### 2016-05-30 prob.tex
prob.tex \subsection{Measuring Probabilities: Buffon's Needle Problem} update the law of large numbers...

In previous section, we assume the probability of each event is known
a priori. In reality, we seldom know much about events, but we assume
each event~$E$ has a probability~$\pmeas(E)$. $\pmeas(E)$ could
be approximated by the relative frequency~$\frac{1}{N}\sum_{i}x_{i}$,
where $x_{i}$ is the outcome of $i$-th trial within total $N$ independent
trials. This fact is called by the law of large numbers~\cite{Bernoulli1713,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

>>>>

In previous section, the probability of each event is known
a priori. In reality, we seldom know much about events, but we could still assume
each event~$E$ has a probability~$\pmeas(E)$. If we want to know the
probability~$\pmeas(E)$, we could run $N$ independent trials. Let $x_{i}$ denote
whether the event~$E$ occurs in the $i$-th trial or not, then $\pmeas(E)$ could
be approximated to given accuracy by the relative
frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability converging to one as
$N$ goes to infinity. This fact is called the law of large numbers~\cite{Bernoulli1713,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
